Manuscript

### 2015-02-12 inst/simulation/manuscript.Rmd
...

getMeanPopulationSizes <- function(populationSizes) {
  meanPopulationSizes <- ddply(populationSizes, .(scenario, modelName), function(x) {
    x <- data.frame(True=mean(x$Observed), Estimated=mean(x$Estimated), Scenario=x$scenario[1])
    if (is.infinite(x$True)) x$True <- NA
    if (is.infinite(x$Estimated)) x$Estimated <- NA
    return(x)
  })
  return(meanPopulationSizes)
}

@@

plotLogPopulationSize <- function(size, meanSize, modelName, xlim, ylim) {
  library(ggplot2)
  library(scales)  
  size$Scenario <- prettyScenario(size$Scenario)
  meanSize$Scenario <- prettyScenario(meanSize$Scenario)

@@

meanPopulationSizes  <- getMeanPopulationSizes(populationSizes)
logPopulationSizes <- getLogPopulationSizes(populationSizes)
logMeanPopulationSizes  <- getMeanPopulationSizes(logPopulationSizes)

meanPopulationSizes2000  <- getMeanPopulationSizes(populationSizes2000)
logPopulationSizes2000 <- getLogPopulationSizes(populationSizes2000)
logMeanPopulationSizes2000  <- getMeanPopulationSizes(logPopulationSizes2000)

meanPopulationSizes10Days  <- getMeanPopulationSizes(populationSizes10Days)
logPopulationSizes10Days <- getLogPopulationSizes(populationSizes10Days)
logMeanPopulationSizes10Days  <- getMeanPopulationSizes(logPopulationSizes10Days)
```

@@

xlim <- log10(10^c(2,4)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[1]), subset(logMeanPopulationSizes2000, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[3]), subset(logMeanPopulationSizes2000, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[4]), subset(logMeanPopulationSizes2000, modelName==modelNames[4]), modelName=modelNames[4], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b3.png", width=8, height=4)

@@

```{r table-1abc}
getPopulationSizesTable <- function(populationSizes, meanPopulationSizes, overEstimate, full=F, file, ...) {
  library(plyr)
  x <- ddply(populationSizes, .(Scenario, modelName), function(x, overEstimate) {
    failed <- round((sum(x$Estimated >= overEstimate) / nrow(x)) * 100)
    if (x$modelName == "FMPModel") failed <- NA
    if (any(abs(x$Estimated) == Inf)) return(data.frame(Intercept=NA, Slope=NA, R2=NA, Failed=failed, MeanProp=NA, SDProp=NA))
    y <- lm(Estimated~Observed, x)
    prop.mean <- mean(x$Estimated/x$Observed)
    prop.sd <- sd(x$Estimated/x$Observed)
    return(data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2), MeanProp=prop.mean, SDProp=prop.sd, Failed=failed))
  }, overEstimate=overEstimate)

@@

table1 <- getPopulationSizesTable(populationSizes, meanPopulationSizes, overEstimate=2000)
logTable1 <- getPopulationSizesTable(logPopulationSizes, logMeanPopulationSizes, overEstimate=log10(2000+1))
logTable1$MeanProp <- table1$MeanProp; logTable1$SDProp <- table1$SDProp;

table2 <- getPopulationSizesTable(populationSizes2000, meanPopulationSizes2000, overEstimate=20000)
logTable2 <- getPopulationSizesTable(logPopulationSizes2000, logMeanPopulationSizes2000, overEstimate=log10(20000+1))
logTable2$MeanProp <- table2$MeanProp; logTable2$SDProp <- table2$SDProp;

table3 <- getPopulationSizesTable(populationSizes10Days, meanPopulationSizes10Days, overEstimate=2000)
logTable3 <- getPopulationSizesTable(logPopulationSizes10Days, logMeanPopulationSizes10Days, overEstimate=log10(2000+1))
logTable3$MeanProp <- table3$MeanProp; logTable3$SDProp <- table3$SDProp;

@@

```{r table-2}
intersections <- getIntersections(scenarios)
intersections2000 <- getIntersections(scenarios=paste0(scenarios, "combined"))
intersections10days <- getIntersections(scenarios=paste0(scenarios, "10days"))
intersections <- plyr::join(populationSizes, intersections)
intersections2000 <- plyr::join(populationSizes2000, intersections2000)
intersections10days <- plyr::join(populationSizes10Days, intersections10days)
i.stat <- function(x) data.frame(o.mean=mean(x$Observed), o.sd=sd(x$Observed), e.mean=mean(x$Estimated), e.sd=sd(x$Estimated),
                                 pp.mean=round(mean(x$Estimated/x$Observed), 2), pp.sd=round(sd(x$Estimated/x$Observed), 2),
                                 i.mean=mean(x$intersections), i.sd=sd(x$intersections), ip.mean=round(mean(x$intersections/x$Observed),2), ip.sd=round(sd(x$intersections/x$Observed),2))
ddply(intersections, .(Scenario, modelName), i.stat)
ddply(intersections2000, .(Scenario, modelName), i.stat)
ddply(intersections10days, .(Scenario, modelName), i.stat)

>>>>

cutoff <- 1000
cutoffPopulationSizes <- function(populationSizes, cutoff=Inf) subset(populationSizes, Estimated <= cutoff)

getMeanPopulationSizes <- function(populationSizes) {
  library(plyr)
  meanPopulationSizes <- ddply(populationSizes, .(scenario, modelName), function(x) {
    x <- data.frame(True=mean(x$Observed), Estimated=mean(x$Estimated), Scenario=x$scenario[1])
    if (is.infinite(x$True)) x$True <- NA
    if (is.infinite(x$Estimated)) x$Estimated <- NA
    return(x)
  })
  return(meanPopulationSizes)
}

@@

plotLogPopulationSize <- function(size, modelName, xlim, ylim, cutoff) {
  library(ggplot2)
  library(scales)  
  size$Scenario <- prettyScenario(size$Scenario)
  meanSize <- getMeanPopulationSizes(size)
  meanSize$Scenario <- prettyScenario(meanSize$Scenario)

@@

meanPopulationSizes  <- getMeanPopulationSizes(cutoffPopulationSizes(populationSizes, cutoff))
logPopulationSizes <- getLogPopulationSizes(cutoffPopulationSizes(populationSizes, cutoff))
logMeanPopulationSizes  <- getMeanPopulationSizes(logPopulationSizes)

meanPopulationSizes2000  <- getMeanPopulationSizes(cutoffPopulationSizes(populationSizes2000, 10*cutoff))
logPopulationSizes2000 <- getLogPopulationSizes(cutoffPopulationSizes(populationSizes2000, 10*cutoff))
logMeanPopulationSizes2000  <- getMeanPopulationSizes(logPopulationSizes2000)

meanPopulationSizes10Days  <- getMeanPopulationSizes(cutoffPopulationSizes(populationSizes10Days, cutoff))
logPopulationSizes10Days <- getLogPopulationSizes(cutoffPopulationSizes(populationSizes10Days, cutoff))
logMeanPopulationSizes10Days  <- getMeanPopulationSizes(logPopulationSizes10Days)
```

@@

#xlim <- log10(10^c(2,4)); ylim <- xlim
xlim <- log10(10^c(0,4)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[1]), subset(logMeanPopulationSizes2000, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[3]), subset(logMeanPopulationSizes2000, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[4]), subset(logMeanPopulationSizes2000, modelName==modelNames[4]), modelName=modelNames[4], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b3.png", width=8, height=4)

@@

```{r table-1abc}
getPopulationSizesTable <- function(populationSizes, meanPopulationSizes, overEstimate, full=F, file, ...) {
  library(plyr)
  x <- ddply(populationSizes, .(Scenario, modelName), function(x, overEstimate) {
    failed <- round((sum(x$Estimated > overEstimate) / nrow(x)) * 100)
    x <- subset(x, Estimated <= overEstimate)
    if (x$modelName[1] == "FMPModel") failed <- NA
    if (any(abs(x$Estimated) == Inf)) return(data.frame(Intercept=NA, Slope=NA, R2=NA, Failed=failed, MeanProp=NA, SDProp=NA))
    y <- lm(Estimated~Observed, x)
    prop.mean <- mean(x$Estimated/x$Observed)
    prop.sd <- sd(x$Estimated/x$Observed)
    return(data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2), MeanProp=prop.mean, SDProp=prop.sd, Failed=failed))
  }, overEstimate=overEstimate)

@@

table1 <- getPopulationSizesTable(populationSizes, meanPopulationSizes, overEstimate=cutoff)
logTable1 <- getPopulationSizesTable(logPopulationSizes, logMeanPopulationSizes, overEstimate=log10(cutoff+1))
logTable1$MeanProp <- table1$MeanProp; logTable1$SDProp <- table1$SDProp; logTable1$Failed <- table1$Failed

table2 <- getPopulationSizesTable(populationSizes2000, meanPopulationSizes2000, overEstimate=10*cutoff)
logTable2 <- getPopulationSizesTable(logPopulationSizes2000, logMeanPopulationSizes2000, overEstimate=log10(10*cutoff+1))
logTable2$MeanProp <- table2$MeanProp; logTable2$SDProp <- table2$SDProp; logTable2$Failed <- table2$Failed

table3 <- getPopulationSizesTable(populationSizes10Days, meanPopulationSizes10Days, overEstimate=cutoff)
logTable3 <- getPopulationSizesTable(logPopulationSizes10Days, logMeanPopulationSizes10Days, overEstimate=log10(cutoff+1))
logTable3$MeanProp <- table3$MeanProp; logTable3$SDProp <- table3$SDProp; logTable3$Failed <- table3$Failed

@@

```{r table-2}
intersections <- getIntersections(scenarios)
intersections2000 <- getIntersections(scenarios=paste0(scenarios, "combined"))
intersections10days <- getIntersections(scenarios=paste0(scenarios, "10days"))
intersectionsx <- plyr::join(populationSizes, intersections)
intersections2000x <- plyr::join(populationSizes2000, intersections2000)
intersections10daysx <- plyr::join(populationSizes10Days, intersections10days)
i.stat <- function(x) data.frame(o.mean=mean(x$Observed), o.sd=sd(x$Observed), e.mean=mean(x$Estimated), e.sd=sd(x$Estimated),
                                 pp.mean=round(mean(x$Estimated/x$Observed), 2), pp.sd=round(sd(x$Estimated/x$Observed), 2),
                                 i.mean=mean(x$intersections), i.sd=sd(x$intersections), ip.mean=round(mean(x$intersections/x$Observed),2), ip.sd=round(sd(x$intersections/x$Observed),2))
ddply(intersectionsx, .(Scenario, modelName), i.stat)
ddply(intersections2000x, .(Scenario, modelName), i.stat)
ddply(intersections10daysx, .(Scenario, modelName), i.stat)

rer.stat <- function(x) data.frame(RERMean=round(mean(x$intersections/x$Observed),2), RERSD=round(sd(x$intersections/x$Observed),2))
ddply(intersectionsx, .(Scenario), rer.stat)
ddply(intersections2000x, .(Scenario), rer.stat)
ddply(intersections10daysx, .(Scenario), rer.stat)
#writeTable(subset(logTable1, Model != "VT"), "table-1a.docx", context)
